Under this section, the different cross functional teams used within the frames for the project is described further. Also, more general processes regarding the cross-functional teams are described.
\subsection{The creation of cross-functional teams \& it's reasons}
The usage of cross-functional teams is an essential part of the project and one of the corner stones for an effective progression of tasks. Through the usage of cross-functional teams, information and knowledge spread in different departments can be pooled together in order to pursue a task. The creation of cross-functional teams can happen in two different ways:

\begin{itemize}
    \item The management sees the need of a cross-functional team even before a certain task is started and connects organization members from the departments / groups concerned for the task. 
    \item The people performing the task sees the need of a cross-functional team while working with the task since they find their information or knowledge for the subject not being enough to fulfill and finish the task.
\end{itemize}

The common denominator is that the cross-functional teams always are created in order to enhance the execution of a task and/or to bring people with certain knowledge and/or information together. \\

The cross-functional teams are later disassembled when the task intended for the cross-functional team to perform, is finished. The members of the cross-functional team will then go back to its ordinary working group and co-work with the people in the native group. 

\subsection{Developers \& Validation}
The development team is working in several cross functional teams together with the validation team when it comes to developing appropriate and valuable tests. Also, the results of these tests has to be communicated from the validation team to the development team in order to enhance the product in the correct direction. For this reason, a cross-functional team is created. Our test leader, Gustav Karlsson, has a continuous discussion with our lead developer, Filip Eriksson, in order to be updated on what software that's currently being developed and is testable. As mentioned above, the validation team reports the test result to Filip Eriksson in order to be able to correct any bugs found under testing. This cross-functional team is mounted in the beginning of the development phase and demounted in the end of the development phase / at the time for delivery. Emil Strömberg, our integrator, works with Gustav Karlsson in order to introduce tests in the CI/CD pipeline. 

\subsection{Developers \& Analysis}
The development team is working in cross-functional teams with the analysts when mapping the requirements to the product backlog and its specific tasks. Furthermore, this cross-functional team also works with making sure that the product being developed by the development team actually meets the requirements set up by the analysts and the customer. By continuously following up this process, time can be saved since minor issues can be found before being escalated into major problems. Theses cross-functional teams are to be active from the start of the development phase until delibery of the product. 

\subsection{Developers \& UX/Design Team}
The UX/Design Team is responsible for developing and maintaining the Hi-Fi prototype in line with the requirements mapped by the analyst team. The Hi-Fi prototype is used by the development team to serve as a blue print for how the final product are to function and look. In the process of interpreting the Hi-Fi prototype when coding, the UX / design team is available for clarifications and questions. This cross-functional team work will ease the process of developing the entire product and is planned to be in use during the entire development phase of the project. 

\subsection{Management \& Development Team}
When planning the development sprints, the management team is involved to provide information regarding external deadlines and time frames. During development, Filip Eriksson continuously reports the progress of the system every week to the management team. 
